A family of accessibility measures derived from spatial interaction principles

### 2025-04-07 paper/manuscript.qmd
Singly-constrained

Similar to @eq-total-population-balancing-factor in transposing the origins and destinations, we can define a *singly-constrained* measure of market potential that preserves the known population (i.e., the mass weight at the origin $W_i^(1)$ is now represented by $O_i$). In it's per-capita expression, i.e., equivalent to 2SFCA, this constrained concept of market potential been used to express "facility crowdedness" as in @wang_inverted_2018. <!-- Anything else like this in the literature?-->

>>>>

Similar to @eq-total-population-balancing-factor in transposing the origins and destinations, we can define a *singly-constrained* measure of market potential that preserves the known population (i.e., the mass weight at the origin $W_i^{(1)}$ is now represented by $O_i$). In it's per-capita expression, i.e., equivalent to 2SFCA, this constrained concept of market potential been used to express "facility crowdedness" as in @wang_inverted_2018. <!-- Anything else like this in the literature?-->
